EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
BE

\begin{abstract}
  \EVOSUITE is a search-based tool that automatically generates unit
  tests for Java code.  This paper summarizes the results and
  experiences of \EVOSUITE's participation at the fifth unit testing
  competition at SBST 2017, where \EVOSUITE achieved the highest
  overall score.
\end{abstract}

@@

Like in the 2016 competition, tools were called with different time
budgets. We used the same strategy as for the previous
competition~\cite{evosuiteAtSbst2016} to distribute the overall time
budget onto the different phases of \EVOSUITE (e.g., initialization,
search, minimization, assertion generation, compilation check, removal
of flaky tests). That is, 50\% of the time was allocated to the
search, and the rest was distributed equally to the remaining
phases.

@@

% Although coverage generally increased with higher time budgets, there
% are instances where this expected behaviour was not observed,
% specially for $budget=300s$, where the average across benchmarks
% decreased. This is possibly due to crashes or out-of-memory runtime
% errors. For instance, \EVOSUITE failed to generate any test suite in
% one out of three runs of OKHTTP-2 and RE2J-7 due to an
% \textit{out-of-memory error}, and in all executions of LA4J-3 and
% LA4J-7 due to a \textit{state exception}. In order to evaluate a
% fitness function, each test case evolved by the underline GA of
% \EVOSUITE has to be executed. However, its execution could fail due to
% several reasons: state exception (if a test case tries to re-initalize
% EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
% case of a timeout, \EVOSUITE logs the stacktrace of the thread in
% which each test case is executed, which could cause an out-of-memory
% error if the stack trace message is to long. RE2J-7: \TODO{I do not
% understand how a java.lang.OutOfMemoryError could be throw by
% CBranchSuiteFitness.java:145}.
% %
% To avoid low coverage of final classes with private constructors (like
% the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
% to call the default constructor of the class under test. However,
% \TODO{EvoSuite tries to access a field of the cut (which is public
% static final) by using an instance of cut. It's still not clear why}.
% For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
% \EVOSUITE failed due to mocking related issues.

>>>>

\begin{abstract}
  \EVOSUITE is a search-based tool that automatically generates unit
  tests for Java code.  This paper summarises the results and
  experiences of \EVOSUITE's participation at the fifth unit testing
  competition at SBST 2017, where \EVOSUITE achieved the highest
  overall score.
\end{abstract}

@@

Like in the 2016 competition, tools were called with different time
budgets. We used the same strategy as for the previous
competition~\cite{evosuiteAtSbst2016} to distribute the overall time
budget onto the different phases of \EVOSUITE (e.g., initialisation,
search, minimisation, assertion generation, compilation check, removal
of flaky tests). That is, 50\% of the time was allocated to the
search, and the rest was distributed equally to the remaining
phases.

@@

% Although coverage generally increased with higher time budgets, there
% are instances where this expected behaviour was not observed,
% specially for $budget=300s$, where the average across benchmarks
% decreased. This is possibly due to crashes or out-of-memory runtime
% errors. For instance, \EVOSUITE failed to generate any test suite in
% one out of three runs of OKHTTP-2 and RE2J-7 due to an
% \textit{out-of-memory error}, and in all executions of LA4J-3 and
% LA4J-7 due to a \textit{state exception}. In order to evaluate a
% fitness function, each test case evolved by the underline GA of
% \EVOSUITE has to be executed. However, its execution could fail due to
% several reasons: state exception (if a test case tries to re-initialise
% EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
% case of a timeout, \EVOSUITE logs the stacktrace of the thread in
% which each test case is executed, which could cause an out-of-memory
% error if the stack trace message is to long. RE2J-7: \TODO{I do not
% understand how a java.lang.OutOfMemoryError could be throw by
% CBranchSuiteFitness.java:145}.
% %
% To avoid low coverage of final classes with private constructors (like
% the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
% to call the default constructor of the class under test. However,
% \TODO{EvoSuite tries to access a field of the cut (which is public
% static final) by using an instance of cut. It's still not clear why}.
% For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
% \EVOSUITE failed due to mocking related issues.
